\bf On semidefinite-representable sets over valuation fields

### 2025-05-18 article/paper_padic_spec.tex
commit by Simone

We conclude by the following Lemma:
\begin{lemma}\label{solutions}
  Let $(S,b',c') \in K^{d\times n} \times K^d \times K^n$ be as in \Cref{solsLP}.
  Let $\lambda = -\sum_{i=1}^r c'_i \frac{b'_i}{s_i}$ and $v = \min\limits_{1\le i\le r} \val \frac{c'_{i}}{s_{i}}$.
\end{lemma}
\begin{proof}
The feasible set $\PP' = \{y \in K^n : Sy+b' \geq 0\}$ of the diagonal LP can be written as the set of vectors
$y \in K^n$ that verifies $s_i y_i + b'_i \in \OK$ for $i=1,...,r$ {\it i.e.}:
$$
\PP' = \left\{\left[\begin{smallmatrix} y_1\\ \vdots\\ y_n \end{smallmatrix}\right] \in K^n :
y_i \in -\frac{b'_i}{s_i} + \frac{1}{s_i} \OK, 1\le i\le r\right\}.
$$

>>>>

We conclude by giving explicit solutions to the reduced \eqref{LP}:

\begin{lemma}\label{solutions}
  Assume \eqref{LP} with data $(S,b',c',{\bf 0}, 0)$ be as in \Cref{solsLP} is feasible,
  with feasible set $\PP' = \{y \in K^n : Sy+b' \geq 0\}$.
  Let $\lambda = -\sum_{i=1}^r c'_i b'_i/s_i$ and $v = \min_{1\le i\le r} \val (c'_i/s_i)$.
  If $\val \lambda < v$, the minimum is $\val \lambda$ and is attained on every $x \in \mathcal{P}'$;
  if $\val \lambda \geq v$, the minimum is $v$ and is attained on ${\bf e}_i = (0,\ldots,0,1,0,\ldots,0}$.
\end{lemma}
\begin{proof}
The feasible set $\PP' = \{y \in K^n : Sy+b' \geq 0\}$ of the diagonal LP can be written as the set of vectors
$y \in K^n$ that verifies $s_i y_i + b'_i \in \OK$ for $i=1,...,r$ {\it i.e.}:
$$
\PP' = \left\{\left[\begin{smallmatrix} y_1\\ \vdots\\ y_n \end{smallmatrix}\right] \in K^n :
y_i \in -\frac{b'_i}{s_i} + \frac{1}{s_i} \OK, 1\le i\le r\right\}.
$$
